### 2023-05-08 nondirectional_ms_2023.Rmd
last updates to Rmd file and related figures to adopt to the changes in the shared doc

```{r run-analyses, include=FALSE}
# run all analyses. The outputs are later used in the script
# to preprocess all datasets source the preprocessing script,
# sourcing this script will also download the up-to-date versiob of the confidence database from OSF (not the version used for analysis in this paper).
# source('datasets\\run_preprocessing.R')
# run all analysis on the preprocessed datasets
source('datasets_analysis\\run_all_analyses.R')

@@

# the analysis and simulations for appendix A.
# to run the analysis again, uncomment the (commented) run_appendixA line and comment the read.csv line which reads the results of an existing simulations run.
source('appendix\\appendix_A.R')
appendixA_res <- run_appendixA(apndxA_conf_FAs, apndxA_conf_sensitivity)
# appendixA_res <- read.csv('appendix\\results\\2023-05-04_12_33_43Appendix_A_QUID_OANOVA.csv')

# the analysis and simulations for appendix B.
# to run the analysis again, uncomment the (commented) run_appendixB line and comment the read.csv line which reads the results of an existing simulations run (keeping the save_plot_appendixB line.
source('appendix\\appendix_B.R')
appendixB_res <- run_appendixB(apndx_b_conf)
# appendixB_res <- read.csv('appendix\\results\\2023-05-05_04_27_22Appendix_B.csv')
save_plot_appendixB(appendixB_res)
```

@@

(ref:figure4caption) Sign-consistency test results for null directional effects from different cognitive psychology fields. Turquoise and purple markers indicate the outcomes for datasets from the Confidence Database [@rahnev2020a]  that were analysed to reveal differences in confidence and metacognitive sensitivity between responses, respectively. Orange markers indicate the outcomes for effects from various cognitive psychology studies. Finally, for comparison purposes, we also plot here in red the results of the studies on unconscious processing (N=`r n_empiric_ns`), reported in the previous section. Lower panel: each point depicts the $log_{10}$ transformed p-values obtained by the sign-consistency test (x-axis) and a directional sign-flipping test (y-axis; datasets were filtered to exclude significant directional effects, hence the minimal directional p-value for all datasets is $\alpha=.05$). Upper panel: The p-values density distributions that summarize the results in the lower panel for datasets in each field. 
```{r figure4, out.width="100%", fig.cap = "(ref:figure4caption)"}
# figure 4 was edited in Illustrator, the raw figure is located in 'figures//plots'
knitr::include_graphics("figures//plots//figure4.PNG")
```

>>>>

```{r run-analyses, include=FALSE}
# run all analyses. The outputs are later used in the script
# to preprocess all datasets source the preprocessing script,
# sourcing this script will also download the up-to-date versiob of the confidence database from OSF (not the version used for analysis in this paper).
# source('datasets\\run_preprocessing.R')
# run all analysis on the preprocessed datasets
# source('datasets_analysis\\run_all_analyses.R')

@@

# the analysis and simulations for appendix A.
# to run the analysis again, uncomment the (commented) run_appendixA line and comment the read.csv line which reads the results of an existing simulations run.
source('appendix\\appendix_A.R')
# appendixA_res <- run_appendixA(apndxA_conf_FAs, apndxA_conf_sensitivity)
appendixA_res <- read.csv('appendix\\results\\2023-05-07_09_00_08Appendix_A_QUID_OANOVA.csv')

# the analysis and simulations for appendix B.
# to run the analysis again, uncomment the (commented) run_appendixB line and comment the read.csv line which reads the results of an existing simulations run (keeping the save_plot_appendixB line.
source('appendix\\appendix_B.R')
# appendixB_res <- run_appendixB(apndx_b_conf)
appendixB_res <- read.csv('appendix\\results\\2023-05-08_00_56_10Appendix_B.csv')
save_plot_appendixB(appendixB_res)
```

@@

(ref:figure4caption) Sign-consistency test results for null directional effects from different cognitive psychology fields. Turquoise and purple markers indicate the outcomes for datasets from the Confidence Database [@rahnev2020a]  that were analysed to reveal differences in confidence and metacognitive sensitivity between responses, respectively. Orange markers indicate the outcomes for effects from various cognitive psychology studies. Finally, for comparison purposes, we also plot here in red the results of the studies on unconscious processing (N=`r n_empiric_ns`), reported in the previous section. Lower panel: each point depicts the $log_{10}$ transformed p-values obtained by the sign-consistency test (x-axis) and a directional sign-flipping test (y-axis; datasets were filtered to exclude significant directional effects, hence the minimal directional p-value for all datasets is $\alpha=.05$). Upper panel: The p-values density distributions that summarize the results in the lower panel for datasets in each field. 
```{r figure4, out.width="100%", fig.cap = "(ref:figure4caption)"}
# figure 4 was edited in Illustrator according to the svg file generated by sourcing the figure4.R script, the raw figure is located in 'figures//plots'
knitr::include_graphics("figures//plots//figure4.PNG")
```
